---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# targencoding

```{r, echo = FALSE} 
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version']) 
version <- gsub('-', '.', version) 
```

<!-- badges: start -->
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![packageversion](https://img.shields.io/badge/package%20version-`r version`-orange.svg)](commits/master)
<!-- badges: end -->

**targencoding** contain extra steps for the [recipes](https://recipes.tidymodels.org) package for using target encoding (or effect or likelihood encoding) for categorical variables during preprocessing.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("abichat/targencoding")
```
## Target encoding by the mean

`step_encode_mean()` will replace the levels of a categorical variable by the means of the outcome variable for each level.

```{r example, message=FALSE}
library(recipes)
library(targencoding)
data("penguins", package = "modeldata")
penguins
```

```{r}
rec <- recipe(body_mass_g ~ ., data = penguins) %>%
  step_encode_mean(all_nominal(), outcome = "body_mass_g") %>%
  prep()
juice(rec)
```

To get informations about the step:

```{r}
tidy(rec, 1)
```


